Cross-relaxation in dense ensembles of NV centers and application to magnetometry

### 2022-12-02 Talks/Soutenance 2022/presentation.tex
fatiguééé
tata

\usetheme{Malmoe}
\usecolortheme{seahorse}

\begin{document}
\begin{frame}
\maketitle
%\begin{center}
%\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
%\end{center}
\end{frame}

@@

\subsection{Quantum sensing and magnetometry}
\begin{frame}{Quantum sensing and metrology}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_metrology}
\end{frame}

\begin{frame}{Magnetometry key parameters}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_magnetometer_size}
\end{frame}

\begin{frame}{Sate of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_bare}
\end{frame}

@@

\begin{frame}{Sate of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_SQUID}
\end{frame}

\begin{frame}{Sate of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_NV}
\end{frame}

\subsection{NV center magnetometry}
\begin{frame}{NV center overview}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_rapido}
\end{frame}

\begin{frame}{NV center magnetometry sensitivity}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_limite_sensi}
\end{frame}

\section{Diamond and NV centers in practice}
\subsection{Diamond properties}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

@@

@@

\subsection{NV center energy levels}
\begin{frame}{The NV center energy levels}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_levels_1}
\end{frame}

@@

\subsection{Basic experiment with NV centers}
\begin{frame}{Experimental setup}
\centering
\includegraphics[width=0.9\textwidth,height=0.85\textheight,keepaspectratio]{Slide_setup}
\end{frame}

@@

\begin{frame}{ODMR with NV ensemble}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_ODMR_8_classes}
\end{frame}

\begin{frame}{Transverse magnetic field effect}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_champs_transverse}
\end{frame}

@@

\section{Depolarization mechanisms in dense NV ensemble}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation}
\end{frame}

@@

\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro}
\end{frame}

@@

\begin{frame}{Zero field depolarization sources (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie}
\end{frame}

@@

\begin{frame}{Angular sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_angular_sensitivity}
\end{frame}

\begin{frame}{Conclusion}

\end{document}

>>>>

\usetheme{Malmoe}
\usecolortheme{seahorse}
\setcounter{tocdepth}{1}

\begin{document}
\begin{frame}
\maketitle
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
\end{center}
\end{frame}

\begin{frame}{Context of my PhD}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_contexte_f-4}
\end{frame}

\begin{frame}{Context of my PhD}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_contexte_f-3}
\end{frame}

\begin{frame}{Context of my PhD}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_contexte_f-2}
\end{frame}

\begin{frame}{Context of my PhD}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_contexte_f-1}
\end{frame}

\begin{frame}{Context of my PhD}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_contexte_f}
\end{frame}

@@

\subsection{Quantum sensing}
\begin{frame}{Quantum sensing and metrology}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_metrology}
\end{frame}

\subsection{Magnetometry}
\begin{frame}{Key properties of magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_magnetometer_size_f-2}
\end{frame}

\begin{frame}{Key properties of magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_magnetometer_size_f-1}
\end{frame}

\begin{frame}{Key properties of magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_magnetometer_size_f}
\end{frame}

\begin{frame}{Sate of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_bare_1}
\end{frame}

@@

\begin{frame}{State of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_SQUID}
\end{frame}

\begin{frame}{State of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_NV_n-3}
\end{frame}

\begin{frame}{State of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_NV_n-2}
\end{frame}

\begin{frame}{State of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_NV_n-1}
\end{frame}

\begin{frame}{State of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_NV_n}
\end{frame}

\begin{frame}{State of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_NV_n+1}
\end{frame}

\begin{frame}{State of the art magnetometers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_quantum_magnetometers_NV_n+2}
\end{frame}

%\begin{frame}{NV center overview}
%\centering
%\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_rapido}
%\end{frame}

\section{NV centers and diamonds in practice}
\subsection{Diamond properties}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

\begin{frame}{Colored centers in diamond}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide diamant_0}
\end{frame}

@@

\begin{frame}{Synthetic diamond and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_fab_sample-3}
\end{frame}

\begin{frame}{Synthetic diamond and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_fab_sample-2}
\end{frame}

\begin{frame}{Synthetic diamond and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_fab_sample-1}
\end{frame}

@@

\subsection{NV center energy levels}
\begin{frame}{The NV center energy levels}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_levels_3}
\end{frame}

%\begin{frame}{The NV center energy levels}
%\centering
%\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_levels_2}
%\end{frame}

\begin{frame}{The NV center energy levels}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_levels_1}
\end{frame}

@@

\subsection{Basic experiment with NV centers}
\begin{frame}{Experimental setup}
\centering
\includegraphics[width=0.9\textwidth,height=0.85\textheight,keepaspectratio]{Slide_setup_-4}
\end{frame}

\begin{frame}{Experimental setup}
\centering
\includegraphics[width=0.9\textwidth,height=0.85\textheight,keepaspectratio]{Slide_setup_-3}
\end{frame}

\begin{frame}{Experimental setup}
\centering
\includegraphics[width=0.9\textwidth,height=0.85\textheight,keepaspectratio]{Slide_setup_-2}
\end{frame}

\begin{frame}{Experimental setup}
\centering
\includegraphics[width=0.9\textwidth,height=0.85\textheight,keepaspectratio]{Slide_setup_-1}
\end{frame}

\begin{frame}{Experimental setup}
\centering
\includegraphics[width=0.9\textwidth,height=0.85\textheight,keepaspectratio]{Slide_setup}
\end{frame}

\begin{frame}{Optically detected magnetic resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.80\textheight,keepaspectratio]{Slide_ODMR_0_-3}
\end{frame}

\begin{frame}{Optically detected magnetic resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.80\textheight,keepaspectratio]{Slide_ODMR_0_-2}
\end{frame}

\begin{frame}{Optically detected magnetic resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.80\textheight,keepaspectratio]{Slide_ODMR_0_-1}
\end{frame}

@@

\begin{frame}{ODMR with NV ensemble: the 4 classes}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_ODMR_8_classes}
\end{frame}

\begin{frame}{Transverse magnetic field effect}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_champs_transverse_allege}
\end{frame}

@@

\section{Depolarization mechanisms in dense NV ensemble}
\subsection{Cross-relaxations}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation}
\end{frame}

@@

\subsection{The fluctuator model}
\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro}
\end{frame}

@@

\subsection{Low field depolarization mechanisms}
\begin{frame}{Zero field depolarization sources (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie}
\end{frame}

\begin{frame}{Angular sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_angular_sensitivity}
\end{frame}
\subsection{Conclusion}
\begin{frame}{Conclusion}

\begin{itemize}
\item The use of NV center ensemble for magnetometry is currently limited by the interactions between the spin defects.
\bigskip
\item Dipole-dipole interaction within dense ensemble of NV centers result in spin depolarization which is exacerbated at low magnetic field.
\bigskip
\item This depolarization can be used to perform microwave-free and orientation-free magnetometry at low magneitc field.
\bigskip
\item the LFDM sensitivity seem to be determined by the double-flips.
\end{itemize}

\section*{Bonus slides}

@@

\begin{frame}{NV center magnetometry sensitivity}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_limite_sensi}
\end{frame}
\end{document}
